Ae. albopictus CPP manuscript

### 2020-07-27 Albopictus_cpp_MS.Rmd
NEE submission

```{r}
#photoperiods on deadline dates
PP_us <- read.csv("deadline465_pp_US.csv", check.names=FALSE) %>% gather(year, deadline_daylength, "1998":"2018", factor_key=FALSE)
PP_jp <- read.csv("deadline465_pp_jp.csv", check.names=FALSE) %>% gather(year, deadline_daylength, "1998":"2018", factor_key=FALSE)
PP_pops<-rbind(PP_us, PP_jp)
PP_pops$year<-as.numeric(PP_pops$year)
```

@@

gdd_all_new<-left_join(gdd_all, cpp_year, by="pop")
gdd_all_new$CPP_YEAR<-as.factor(gdd_all_new$CPP_YEAR)

```{r}
gdd_all_new<-left_join(gdd_all_new, PP_pops, by=c("pop","year"))
```

@@

```{r}
#CPP vs. photoperiod on deadline day
gdd_pp_08 <- ggplot(filter(gdd_all_new, year==2007, CPP_YEAR==2008), aes(x=deadline_daylength, y=Estimate, fill=country)) + scale_fill_manual(values=c("black","gray"), name="Country") + geom_point(size=4, stroke=1, shape=22) + stat_smooth(method=lm, se=FALSE, aes(color=country), linetype="longdash") + scale_color_manual(values=c("black","gray"), name="Country") +
  theme(legend.position=c(.75,.25), text=element_text(size=22),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
    xlab("2007 Deadline Day Length") + ylab("CPP (h), 2008") + ylim(12.3,14.2)

gdd_pp_18 <- ggplot(filter(gdd_all_new, year==2017, CPP_YEAR==2018), aes(x=deadline_daylength, y=Estimate, fill=country)) + scale_fill_manual(values=c("black","gray"), name="Country") + geom_point(size=4, stroke=1, shape=21) + stat_smooth(method=lm, se=FALSE, aes(color=country)) + scale_color_manual(values=c("black","gray"), name="Country") +
  theme(legend.position=c(.75,.25), text=element_text(size=22),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black")) + 
xlab("2017 Deadline Day Length") + ylab("CPP (h), 2018") + ylim(12.3, 14.2)

@@

```{r echo=FALSE, include=FALSE}
#FIG 4
gdd_cpp_plot_decade<-plot_grid(gdd_cpp_interval_08, gdd_cpp_interval_18, nrow=2, labels="AUTO")
#FIG S5
gdd_cpp_plot_year<-plot_grid(gdd_08, gdd_pp_08, gdd_18, gdd_pp_18, nrow=2, labels="AUTO")
```

>>>>

@@

gdd_all_new<-left_join(gdd_all, cpp_year, by="pop")
gdd_all_new$CPP_YEAR<-as.factor(gdd_all_new$CPP_YEAR)
```

@@

@@

```{r echo=FALSE, include=FALSE}
#FIG 4
gdd_cpp_plot_decade<-plot_grid(gdd_cpp_interval_08, gdd_cpp_interval_18, nrow=2, labels="AUTO")
#FIG S5
gdd_cpp_plot_year<-plot_grid(gdd_08, gdd_18, nrow=2, labels="AUTO")
```
